Global adjoint tomography -- Model GLAD-M25 \\ Supplementary Material

### 2020-05-17 main.tex
merge with master and change to png
Updates from Overleaf

Fig.~\ref{fig:psf_tests} shows the results of the four PSF tests we performed for model GLAD-M25.
The first test repeats an analysis performed by~\cite{bozdaug2016global} for GLAD-M15 in the upper mantle underneath Yellowstone.
That test was based on 253 earthquakes,
and Figs.~\ref{fig:psf_tests}a shows our result for the same location based on the current dataset of 1,480 events.
We observe that the 100~km diameter anomaly ---which is smaller than what was used in GLAD-M15--- at 300~km depth is well recovered, with little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and~$c$ (See SOM).
Figs.~\ref{fig:psf_tests}b--d shows the results of PSF tests for larger Gaussian anomalies (with 200~km to 400~km diameters) in the lower mantle beneath Afar,
in the lowermost mantle beneath Easter Island,
and in the mid mantle below Sumatra.
In each case the Gaussian anomaly is well recovered, with minimal tradeoff with other model parameters (See SOM).

>>>>

Fig.~\ref{fig:psf_tests} summarizes the results of the four PSF tests we performed for model GLAD-M25.
The first test repeats an analysis performed by~\cite{bozdaug2016global} for GLAD-M15 in the upper mantle underneath Yellowstone.
That test was based on 253 earthquakes,
and Figs.~\ref{fig:psf_tests}a shows our result for the same location based on the current dataset of 1,480 events.
We observe that the 100~km diameter~$\beta_\mathrm{V}$ anomaly ---which is smaller than what was used in GLAD-M15--- at 300~km depth is well recovered, with little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and~$c$ (see the SOM).
Figs.~\ref{fig:psf_tests}b--d shows the results of PSF tests for larger Gaussian anomalies in isotropic shear wavespeed~$\beta$ (with 200~km to 400~km diameters) in the lower mantle beneath Afar,
in the lowermost mantle beneath Easter Island,
and in the mid mantle below Sumatra.
In each case the Gaussian anomaly is well recovered, with minimal tradeoff with other model parameters (also see the SOM).

### 2020-05-17 supplementary_material.tex
fix figure size issue
Updates from Overleaf

This section summarizes the complete Point Spread Function (PSF) tests conducted as part of this study, including the tradeoff between parameters.
Figs.~\ref{fig:psf_yellowstone}--\ref{fig:psf_usa_east} show the results of PSF tests underneath Yellowstone, Easter Island, Afar, Sumatra, and two additional locations underneath the United States.
Finally, Fig.~\ref{fig:patern1200} shows the results of a patterned resolution test at a depth of 1,200~km.
Each figure shows the original Gaussian perturbation in vertically polarized shear wavespeed, $\mathsf{\Delta}\mathsf{m}$\,, as well as the action of the Hessian on this model perturbation, $\mathsf{H}\mathsf{\Delta}\mathsf{m}$\,.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/easter.pdf}
  \caption{\small{PSF test for Easter Island.
  A 300~km diameter negative Gaussian anomaly is placed at a depth of 2,500~km beneath Easter Island.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.}}
  \label{fig:psf_easter}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/afar.pdf}
  \caption{\small{PSF test for Afar.
    A 400~km diameter negative Gaussian anomaly is placed at a depth of 2,000~km beneath Afar.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_afar}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/su.pdf}
  \caption{\small{PSF test for Sumatra.
    A 200~km diameter positive Gaussian anomaly is placed at a depth of 900~km beneath Sumatra.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_su}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/usa_east.pdf}
  \caption{\small{PSF test underneath the eastern United States.
    A 250~km diameter positive Gaussian anomaly is placed at a depth of 1500~km beneath the eastern US.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_usa_east}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.95\textwidth]{figures/psf/psf-1200km.pdf}
  \caption{\small{Patterned PSF test at a depth of 1,200~km,
  where the model is isotropic.
    An alternating positive and negative pattern of 100~km diameter Gaussian anomalies in shear wavespeed is placed at a depth of 1,200~km.
  Left: input pattern for~$\beta$.
  Middle: recovered pattern for~$\beta$.
  Right: tradeoff with bulk sound speed~$c$.
  We conclude that there is little tradeoff between~$\beta$ and~$c$, and that the pattern at this mid-mantle depth is reasonably well recovered, both in terms of geometry and in terms of strength.
  }}
  \label{fig:patern1200}
\end{figure}

>>>>

This section summarizes the complete Point Spread Function (PSF) tests conducted as part of this study, including the tradeoff between parameters.
Figs.~\ref{fig:psf_yellowstone}--\ref{fig:psf_usa_east} show the results of PSF tests underneath Yellowstone, Easter Island, Afar, Sumatra, and two additional locations underneath the United States.
Finally, Fig.~\ref{fig:patern1200} shows the results of a patterned resolution test at a depth of 1,200~km.
Each figure shows the original Gaussian perturbation in wavespeed, $\mathsf{\Delta}\mathsf{m}$\,, as well as the action of the Hessian on this model perturbation, $\mathsf{H}\mathsf{\Delta}\mathsf{m}$\,.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/easter.pdf}
  \caption{\small{PSF test for Easter Island.
  A 300~km diameter negative Gaussian anomaly is placed at a depth of 2,500~km beneath Easter Island.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta$ and~$c$.
  }}
  \label{fig:psf_easter}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/afar.pdf}
  \caption{\small{PSF test for Afar.
    A 400~km diameter negative Gaussian anomaly is placed at a depth of 2,000~km beneath Afar.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta$ and~$c$.
  }}
  \label{fig:psf_afar}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/su.pdf}
  \caption{\small{PSF test for Sumatra.
    A 200~km diameter positive Gaussian anomaly is placed at a depth of 900~km beneath Sumatra.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta$ and~$c$.
  }}
  \label{fig:psf_su}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/usa_east.pdf}
  \caption{\small{PSF test underneath the eastern United States.
    A 250~km diameter positive Gaussian anomaly is placed at a depth of 1500~km beneath the eastern US.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta$ and~$c$.
  }}
  \label{fig:psf_usa_east}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.75\textwidth]{figures/psf/psf-1200km.pdf}
  \caption{\small{Patterned PSF test at a depth of 1,200~km,
  where the model is isotropic.
    An alternating positive and negative pattern of 100~km diameter Gaussian anomalies in shear wavespeed is placed at a depth of 1,200~km.
  Left: input pattern for~$\beta$.
  Middle: recovered pattern for~$\beta$.
  Right: tradeoff with bulk sound speed~$c$.
  We conclude that there is little tradeoff between~$\beta$ and~$c$, and that the pattern at this mid-mantle depth is reasonably well recovered, both in terms of geometry and in terms of strength.
  }}
  \label{fig:patern1200}
\end{figure}
